Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-08-01 ms/main.tex
Add new figure
Add Boundaries Graph for Result 2

Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
The next corollary deals with such a condition, followed by a corollary that deals with symmetric horizontal transmission, i.e. $T_A=T_B$.
\\

\begin{corollary}[Condition for cooperation to increase from rarity]
If the initial frequency of the cooperative phenotype if very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
\begin{equation} \label{eq:unequal_transmission_from_rarity}
\begin{aligned}
T_A>T_B \;\; \text{and} \;\; c < \gamma_1, \quad \text{or} \quad
T_A<T_B \;\; \text{and} \;\; \gamma_2<c < \gamma_1. 
\end{aligned}
\end{equation} 
\end{corollary}

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2a.pdf}
    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
    \label{fig:results_a}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2b.pdf}
    \caption{$v=1$, $\alpha = 0$}
    \label{fig:results_b}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2c.pdf}
    \caption{$v=0$}
    \label{fig:results_c}
  \end{subfigure}
  \label{fig:results}
  \caption{
  \textbf{Numerical results for cultural evolution of cooperation.}
  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
  %TODO ic (c), the blue and green got mixed. 
  % TODO have all panels in one row.
  }
\end{figure}

>>>>

Much of the literature on evolution of cooperation focuses on conditions for cooperation to invade a population of defectors.
The next corollary deals with such a condition, followed by a corollary that deals with symmetric horizontal transmission, i.e. $T_A=T_B$.
\\
%%% Figure: Boundries graph of results 2

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2a.pdf}
    \caption{$b=1.3$, $T_A=0.4$, $\alpha = 0.7$}
    \label{fig:results2_a}
    \includegraphics[scale=0.5]{figure2b.pdf}
    \caption{$b=1.3$, $T_A=0.4$, $\alpha = 0$}
    \label{fig:results2_b}
  \end{subfigure}
  \label{fig:results2}
  \caption{\textbf{Boundaries graph} This figure illustrates under what values of $T_A-T_B$ and cost $c$ fixation of cooperates, fixation of defectors or coexistence are possible given where $b$, $\alpha$ and $T_B$ are known.
    Figure \textbf{(a)} illustrates that when $\alpha \neq 0$ fixation of cooperates, fixation of defectors or coexistence are possible. \textbf{(b)} illustrates that when $\alpha=0$ coexistence is not possible, only fixation of one of the phenotypes}
\end{figure}
%%%

\begin{corollary}[Condition for cooperation to increase from rarity]
If the initial frequency of the cooperative phenotype if very close to zero, $\tilde{p}_0 \approx 0$, then its frequency will increase if 
\begin{equation} \label{eq:unequal_transmission_from_rarity}
\begin{aligned}
T_A>T_B \;\; \text{and} \;\; c < \gamma_1, \quad \text{or} \quad
T_A<T_B \;\; \text{and} \;\; \gamma_2<c < \gamma_1. 
\end{aligned}f
\end{equation} 
\end{corollary}

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure3a.pdf}
    \caption{$v=1$, $T_A=T_B=T$, $\alpha \neq 0$}
    \label{fig:results_a}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure3b.pdf}
    \caption{$v=1$, $\alpha = 0$}
    \label{fig:results_b}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure3c.pdf}
    \caption{$v=0$}
    \label{fig:results_c}
  \end{subfigure}
  \label{fig:results}
  \caption{
  \textbf{Numerical results for cultural evolution of cooperation.}
  Shown are dynamics of \textbf{(a-b)} $\tilde{p}$, the frequency of parents with cooperative phenotype $A$; \textbf{(c)} $p'$, the frequency of adults with cooperative phenotype $A$.
  The figure demonstrates fixation of cooperation (green), extinction of cooperation (blue)m and stable co-existence of cooperators and defectors (orange).
  % TODO have all panels in one row.
  }
\end{figure}
